On The Subspace Learning for Network Attack Detection

### 2019-05-27 docs/thesis/thesis.tex
tensor dl motivation
tensor-related works
improving the approach and experiment description
prepare for thesis writing
first deliverable

% class
\documentclass[en, oneside, onehalfspacing]{risethesis}

% packages and configurations
\usepackage{enumitem}
\usepackage{lineno, hyperref}
\usepackage[numbers]{natbib}
\usepackage{babel}
\usepackage{supertabular}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{longtable}
\usepackage{amsthm,amsmath}
\usepackage{mathtools}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{hyperref}

@@

\definecolor{lightgray}{gray}{0.8}
\definecolor{Gray}{gray}{0.9}
\renewcommand{\lstlistingname}{Code}
\renewcommand{\lstlistlistingname}{Lista de Listagens}

@@

\title{Discriminative Sensing Based on Signal Processing for Information Security Analysis}
\date{November/2017}

@@

\include{chapters/1_introduction/introduction}
\include{chapters/2_eigen_similarity/eigen_similarity}
\include{chapters/3_mobile/mobile}
\include{chapters/4_tensor_dl/tensor_dl}
\include{chapters/5_conclusion_future_work/conclusion}

\appendix
\include{chapters/appendix/a_mos/a_mos}
\include{chapters/appendix/b_pca_svm_cfa/pca_svm_cfa}

>>>>

% class
\documentclass[en, oneside, onehalfspacing]{risethesis}
% \usepackage[mathletters]{ucs}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
% table
\usepackage{makecell}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
\definecolor{lightgray}{gray}{0.8}
% packages and configurations
\usepackage{enumitem}
\usepackage{lineno, hyperref}
\usepackage[numbers]{natbib}
\usepackage{babel}
\usepackage{fancybox}
\usepackage{acronym}
\usepackage{array}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{supertabular}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{color, colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{setspace}
\usepackage{placeins}
\usepackage{amsthm,amsmath}
\usepackage{mathtools}

\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
\usepackage{listings}
\usepackage{epstopdf}
\usepackage{subfigure}
\usepackage{courier}
\usepackage{amsfonts}
\usepackage{morefloats}
\usepackage{lipsum}
\usepackage{cleveref}
\usepackage{hyperref}

% appendix
\usepackage{appendix}
\usepackage{hyperref}
\usepackage{cleveref}

@@

\renewcommand{\lstlistingname}{Code}
\renewcommand{\lstlistlistingname}{Lista de Listagens}

@@

\title{On The Subspace Learning for Network Attack Detection}
\date{July/2019}

@@

\include{chapters/1_introduction/introduction}
\include{chapters/2_eigen_similarity/eigen_similarity}
\include{chapters/3_mobile/mobile}
\include{chapters/4_m_rpca/m_rpca}
\include{chapters/5_conclusion_future_work/conclusion}

\appendix
\include{chapters/appendix/a_mos/a_mos}
\include{chapters/appendix/b_pca_svm_cfa/pca_svm_cfa}
\include{chapters/appendix/c_tensor_denoising/c_tensor_denoising}
